---
title: "Introduction (draft)"
#bibliography: references.bib
author: "Niels Vullings"
bibliography: references.bib
---

# Html text stuff
## Justify my text files
Who doesn't want their text files to be justified!
```{r}

# ```{=html}
# <style>
# body {
# text-align: justify;
# font-family: Times;
# }
# </style>
# ```

```

## Tabs galore
For when the start of a paragraph just needs a little nudge 
```{r}
 
# &nbsp; # Wow it is a single space
# &ensp; # My god there are two
# &emsp; # Here we have 4 a.k.a a tab
# &nbsp; *4 # apparently does something different than emsp

```

## Writing texts
Use Visual mode instead of source mode (ctrl + shift + F4 | just click it in the visual button below the save button)

# Basic knitting stuff
```{r, globalsettings, echo=TRUE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()
```

# Klippy code to copy code chunks
```{r klippy, echo=TRUE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
# klippy::klippy(color = 'darkgreen')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

