---
title: "Conclusion & Discussion"
#bibliography: references.bib
author: "Niels Vullings"
bibliography: references.bib
---

```{=html}
<style>
body {
  text-align: justify;
  font-family: Times;
}

h1, .h1, h2, .h2, h3, .h3 {
  margin-top: 24px;
  font-family: Times;
}
</style>
```
```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()



colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
# klippy::klippy(color = 'darkgreen')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

Last compiled on `r format(Sys.time(), '%B, %Y')`

<br>

------------------------------------------------------------------------

# Conclusion

This paper aimed to study how collaboration between sociologists at Radboud University and Utrecht Unversity is determined and influenced by gender inequalities. Particularly, the study aims to see how the prestige of female sociologists influences gender clustering in the collaboration network. Previous studies have proven persisting gender inequalities in (social) science, relating to prestige & job status [@bellotti2022; @wang2023gender; @kim2024persistent], career opportunities[@mulders2024matter], publications [@mcdowell2006a; @bozeman2011men; @kwiek2021gender] and other inequalities. Taking inspiration from the gender homophily principle, I theorized that people prefer to collaborate with others from the same gender, due to gender biases and perceived status differences [@kwiek2021gender; @wang2023gender], which leads to clustered networks in terms of gender, as both men and women prefer to work with other men and women, when given the chance (*Hypothesis 1*). However, as structural differences between male and female scholars decrease due to policy changes, genderclustering of collaboration networks will similarly decrease (*Hypothesis 2*). Lastly, Due to these structural changes, prestige of both male and female sociologists will be evenly distributed [@bellotti2022; @kwiek2021gender; @knobloch2013matilda]. Consequently, sociologists will choose their collaborators less in terms of gender and more in terms of prestige, as proposed by the Matthew effect [@bol2018matthew; @wang2014unpacking]. This will decrease gender clustering in collaboration networks (*Hypothesis 3*).\
  Using webscraped publication data from OpenAlex, I was able to determine the collaborative networks of scholars between 2015-2024. The results of this study did not give a concrete answer to the research question. First of all, a descriptive analysis showed that there is some gender clustering worth noting. This indicates that there is some evidence that supports hypothesis 1. Additionally, this level of clustering seemed to decrease over time, as both gender clustering and the amount of indegrees became more evenly distributed over time. However, this decrease was found not to be significant, which was cause to reject *hypothesis 2.\
*  To investigate how these collaboration networks evolve, this data was analysed with RSiena, a simulation method for studying the evolution of social networks [@ripley2011manual]. Interestingly, preliminary models indicated that difference in gender is positively associated with transitivity, indicating that actors want to close triads with alters from a different gender. This is in contrast with the current literature on the Matilda effect [@bellotti2022; @knobloch2013matilda; @wang2023gender]. However, later models indicated prestige is the only significant determinant of collaborating than gender. Prestige was found to be a determinant for being a preferred collaborator. When looking for a person to collaborate with, actors prefer to send ties to alters who have a higher level of prestige (i.e. having worked on more Q1 publications in a given wave). Similarly, the prestige of female sociologists is also found to be indicator of collaboration. *Hypothesis 3* thus finds some evidence and does not need to be rejected However, as said before, due to the diverse findings of this study, conclusive answers cannot be drawn.\
 As many studies, this study has its limitations. One of the main limitations of the data is the short time frame in which the data was collected. Because the data is still in the process of being collected, it was not possible to have two good size waves that also contained 2022 and 2024. Therefore, wave 1 was very sparse, as most PhD's and postdocs were not yet in the department and therefore (might) not have published anything in the first wave. This means that the density of the network is not due to structural effects of the network, but due to the process in which the data was collected. Having another wave in 2026 will ensure that more scholars are present in both waves and that collaboration networks will be more representative of society. Another data related issue is the lack of focus on structurally determined collaboration. for example, PhD's always collaborate with their promotor during their dissertation. Thus, it would be more accurate if these relations were determined by structural 1's, an option of RSiena which means that these actors are always 1, regardless of the structural effects in the model [@ripley2011manual]. Future research would do well to include these structural ties, as the network would likely have created more representative of how collaboration works in the academic world.\
  Relating to the results, future research should focus on finding more concrete answers to this research question, as the results are not in line with the current literature. Similarly, based on the Goodness of Fit of the dyad census, these models would likely have benefited from some form of dyadic covariate network statistics, as the models were not very well able to correctly estimate the dyadic transitions. This makes sense theorywise, as collaboration indicates that there might be a context apart from the ego that is important to take into account. However, given certain time and knowledge restriction, this was not achievable in this study. Additionally, generalizing this to the larger academic setting might also prove beneficial, as this study only looked at two sociology departments at Dutch universities.\
  Overall, this study showed that the way in which scholars at Dutch Universities collaborate is quite complex and not always easy to model. In sum, while there is clustering in terms of gender in these collaboration networks, it seems to be the case that people prefer to work with scholars who have a higher prestige, be it prestigious female scholars or prestigious male scholars [@bol2018matthew].
