---
title: "Data preparation"
#bibliography: references.bib
author: "Niels Vullings"
bibliography: references.bib
---

```{=html}
<style>
body {
text-align: justify}
</style>
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()



colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
# klippy::klippy(color = 'darkgreen')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

Last compiled on `r format(Sys.time(), '%B, %Y')`

<br>

------------------------------------------------------------------------

# Set up

```{r}
rm(list = ls())

# Libraries
library(tidyverse)  # I assume you already installed this one!
library(igraph)


```

# Load data

```{r}
load("data/processed/soc_data_raw.RData")

load("data/processed/RU_UU_ego.RData")

load("data/processed/RU_UU_works.RData")

```

<br>

------------------------------------------------------------------------

# Data description

## Scholars per university

```{r}

df_ego %>% count(Universiteit1.22)
df_ego %>% count(Universiteit2.22)


df_ego %>% count(Universiteit1.24)
df_ego %>% count(Universiteit2.24)

```

## Functions

```{r}
df_ego %>% group_by(Universiteit1.22) %>% count(Functie.22)

df_ego %>% group_by(Universiteit1.24) %>% count(Functie.24)
```

## Gender

### Gender distribution per University in 22 and 24

```{r}

df_ego %>% group_by(Universiteit1.22) %>% 
  summarise(mean_gender = mean(perc_female, na.rm = TRUE))


df_ego %>% group_by(Universiteit1.24) %>% 
  summarise(mean_gender = mean(perc_female, na.rm = TRUE))

```

### Gender distribution per University and per Function in 22 and 24

!!Important to change function levels to have more meaningful results!!

```{r}
df_ego %>% group_by(Universiteit1.22, Functie.22) %>% 
  summarise(mean_gender = mean(perc_female, na.rm = TRUE))

df_ego %>% group_by(Universiteit1.24, Functie.24) %>% 
  summarise(mean_gender = mean(perc_female, na.rm = TRUE))
```

### TO ADD!!

-   Prestigious publications per university/gender/time

-   Moran's I for network segregation in terms of gender

    -   For 22 and 24 to see how/if networks change

-   Other statistics

    -   Nice descriptives table

    -   Network statistics table (density, betweeness, transitivity etc.)

## Networks
### Make the graph object
```{r}

#---- Wave 2 ----
graph_w1 <- igraph::graph_from_adjacency_matrix(
  soc_data$nets[1,,], #now, I take the second wave
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL
)

#---- Wave 2 ----
graph_w2 <- igraph::graph_from_adjacency_matrix(
  soc_data$nets[2,,], #now, I take the second wave
  mode = c("directed"),
  weighted = NULL,
  diag = FALSE,
  add.colnames = NULL
)

```

### Network Visualisations (Universities)

#### Wave 1 {.tabset}
##### University Colours
```{r, fig.width = 8}

#---- Wave 1 ----
set.seed(234544)
l_w1 <- layout_nicely(graph_w1)

plot(graph_w1, layout = l_w1,
     vertex.color = ifelse(df_ego$Universiteit1.22 == "RU", "red", "gold"), #now, I can use actor attributes for plotting. 
     vertex.label = NA,
     edge.width = 1.8,
     edge.arrow.size =0.5,
     main = "Network of Radboud and Utrecht University Sociologists")
legend("topleft", c("Radboud", "Utrecht University"), pch = c(21,21), col = "#777777", pt.bg = c("red", "gold"), pt.cex = 2,
       cex = 0.8, bty = "n", ncol = 1)

```

##### Better contrast
```{r, fig.width = 8}

#---- Wave 1 ----
set.seed(234544)
l_w1 <- layout_nicely(graph_w1)

plot(graph_w1, layout = l_w1,
     vertex.color = ifelse(df_ego$Universiteit1.22 == "RU", "navy", "darkorange"), #now, I can use actor attributes for plotting. 
     vertex.label = NA,
     edge.width = 1.8,
     edge.arrow.size =0.5,
     main = "Network of Radboud and Utrecht University Sociologists")
legend("topleft", c("Radboud", "Utrecht University"), pch = c(21,21), col = "#777777", pt.bg = c("navy", "darkorange"), pt.cex = 2,
       cex = 0.8, bty = "n", ncol = 1)

```

#### Wave 2 {.tabset}
##### University Colours
```{r, fig.width = 8}
#---- Wave 2 ----
set.seed(234544)
l_w2 <- layout_nicely(graph_w2)

plot(graph_w2, layout = l_w2,
     vertex.color = ifelse(df_ego$Universiteit1.24 == "RU", "red", "gold"), #now, I can use actor attributes for plotting. 
     vertex.label = NA,
     edge.width = 1.8,
     edge.arrow.size = 0.5,
     main = "Network of Radboud and Utrecht University Sociologists")
legend("topleft", c("Radboud", "Utrecht University"), pch = c(21,21), col = "#777777", pt.bg = c("red", "gold"), pt.cex = 2,
       cex = 0.8, bty = "n", ncol = 1)

```

##### Better Contrast
```{r, fig.width = 8}
#---- Wave 2 ----
set.seed(234544)
l_w2 <- layout_nicely(graph_w2)

plot(graph_w2, layout = l_w2,
     vertex.color = ifelse(df_ego$Universiteit1.24 == "RU", "navy", "darkorange"), #now, I can use actor attributes for plotting. 
     vertex.label = NA,
     edge.width = 1.8,
     edge.arrow.size = 0.5,
     main = "Network of Radboud and Utrecht University Sociologists")
legend("topleft", c("Radboud", "Utrecht University"), pch = c(21,21), col = "#777777", pt.bg = c("navy", "darkorange"), pt.cex = 2,
       cex = 0.8, bty = "n", ncol = 1)

```

### Network Visualisations (Gender)
```{r}
# Make a plotable gender variable to fix problems with vertex.shape
df_ego <- df_ego %>% mutate(plot_gen = case_when(perc_female >= 0.80 ~ "Female",
                                                 .default = "Male"))
# df_ego %>% count(plot_gen)
```

#### Wave 1 {.tabset}
##### University Colours
```{r, fig.width = 8}

#---- Wave 1 ----
set.seed(234544)
l_w1 <- layout_nicely(graph_w1)

plot(graph_w1, layout = l_w1,
     vertex.color = ifelse(df_ego$Universiteit1.24 == "RU", "red", "gold"), #now, I can use actor attributes for plotting. 
     vertex.shape = ifelse(df_ego$plot_gen == "Male", "square", "circle"),
     vertex.label = NA,
     edge.width = 2,
     edge.curved = 0.5,
     edge.arrow.size =0.2,
     main = "Gender Distribution of Two Sociology Departments 2022")
legend("topleft", c("Radboud", "Utrecht University", "Male", "Female"), pch = c(21,21,15,20), col = "#777777", pt.bg = c("red", "gold"), pt.cex = 2,
       cex = 0.8, bty = "n", ncol = 1)
```

##### Better Contrast
```{r, fig.width = 8}

#---- Wave 1 ----
set.seed(234544)
l_w1 <- layout_nicely(graph_w1)

plot(graph_w1, layout = l_w1,
     vertex.color = ifelse(df_ego$Universiteit1.24 == "RU", "navy", "darkorange"), #now, I can use actor attributes for plotting. 
     vertex.shape = ifelse(df_ego$plot_gen == "Male", "square", "circle"),
     vertex.label = NA,
     edge.width = 2,
     edge.curved = 0.5,
     edge.arrow.size =0.2,
     main = "Gender Distribution of Two Sociology Departments 2022")
legend("topleft", c("Radboud", "Utrecht University", "Male", "Female"), pch = c(21,21,15,20), col = "#777777", pt.bg = c("navy", "darkorange"), pt.cex = 2,
       cex = 0.8, bty = "n", ncol = 1)
```

#### Wave 2 {.tabset}
##### University Colours
```{r, fig.width = 8}
#---- Wave 2 ----
set.seed(234544)
l_w2 <- layout_nicely(graph_w2)

plot(graph_w2, layout = l_w2,
     vertex.color = ifelse(df_ego$Universiteit1.24 == "RU", "red", "gold"), #now, I can use actor attributes for plotting. 
     vertex.shape = ifelse(df_ego$plot_gen == "Male", "square", "circle"),
     vertex.label = NA,
     edge.width = 2,
     edge.curved = 0.5,
     edge.arrow.size =0.2,
     main = "Gender Distribution of Two Sociology Departments 2022")
legend("topleft", c("Radboud", "Utrecht University", "Male", "Female"), pch = c(21,21,15,20), col = "#777777", pt.bg = c("red", "gold"), pt.cex = 2,
       cex = 0.8, bty = "n", ncol = 1)

```

##### Better Contrast
```{r, fig.width = 8}
#---- Wave 2 ----
set.seed(234544)
l_w2 <- layout_nicely(graph_w2)

plot(graph_w2, layout = l_w2,
     vertex.color = ifelse(df_ego$Universiteit1.24 == "RU", "navy", "darkorange"), #now, I can use actor attributes for plotting. 
     vertex.shape = ifelse(df_ego$plot_gen == "Male", "square", "circle"),
     vertex.label = NA,
     edge.width = 2,
     edge.curved = 0.5,
     edge.arrow.size =0.2,
     main = "Gender Distribution of Two Sociology Departments 2022")
legend("topleft", c("Radboud", "Utrecht University", "Male", "Female"), pch = c(21,21,15,20), col = "#777777", pt.bg = c("navy", "darkorange"), pt.cex = 2,
       cex = 0.8, bty = "n", ncol = 1)

```

<br>

---------------------------------------------------------------------------------------------------- 

