---
title: "Results - RSiena Models"
#bibliography: references.bib
author: "Niels Vullings"
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: 72
---

```{=html}
<style>
body {
text-align: justify;
font-family: Times;
}

h1, .h1, h2, .h2, h3, .h3 {
margin-top: 24px;
font-family: Times;
}
</style>
```
```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
# klippy::klippy(color = 'darkgreen')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{r, echo=FALSE}
rm(list = ls())
```

# Load UDF

```{r}

colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}

fsave <- function(x, file = NULL, location = "./results/processed/") {
  ifelse(!dir.exists("results"), dir.create("data"), FALSE)
  ifelse(!dir.exists("results/processed"), dir.create("results/processed"), FALSE)
  if (is.null(file))
    file = deparse(substitute(x))
  datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
  totalname <- paste(location, datename, file, ".rda", sep = "")
  save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
  load(filename)
  get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
  knitr::kable(x, digits = 2, "html", ...) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
    kableExtra::scroll_box(width = "100%", height = "300px")
}

```

# Load Packages

```{r, warning=FALSE, results='hide', message=FALSE}
packages <- c("tidyverse", "sna", "igraph", "RSiena", "iterators", "doParallel")

fpackage.check(packages)

```

# Load Data

```{r}
# Load Ego data
load("data/processed/RU_UU_ego.RData")

# Load Works data
load("data/processed/RU_UU_works.RData")

# Load raw data for networks
load("data/processed/soc_data_raw.RData")
```

# Make network data for RSiena

```{r}
print(paste0("", dim(soc_data$nets)))

wave_1 <- soc_data$nets[1,,]
diag(wave_1) <- 0

wave_2 <- soc_data$nets[2,,]
diag(wave_2) <- 0

net_soc_array <- array(data = c(wave_1, wave_2), dim = c(dim(wave_1), 2))
dim(net_soc_array)
```

------------------------------------------------------------------------

# Analysis {.tabset}

## Model 0

The Null model, containing reciprocity and density, has a convergence of
0.057 and a Goodness of Fit on the indegree distribution of 0,
indicating that the model fits the data very badly. This makes sense,
given that the model does not include any network statistics. Both
reciprocity and density are significant for an alpha of 0.05. It is
important to mention that significance in RSiena means something
different than in conventional statistics. In normal statistics, such as
OLS-regression, significance of estimates refers to the fact that they
are not 0, In RSiena, however, it refers to the fact that the estimates
were precisely determined [@ripley2011manual]. Going forward with this
chapter, significance will refer to this definition of significance. The
density parameter has a value of -2.44, which means that people
generally do not want to have a dense network. The reciprocity parameter
has a value of 2.24, which means that people like to send ties back to
people who have sent a tie to them.

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Make Siena df ----
mydata_M0 <- sienaDataCreate(net)
```

### Create Effects object

```{r}
myeff_M0 <- getEffects(mydata_M0)
print01Report(mydata_M0, modelname = "./results/Collab_M0")

# ts_dyads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)
# ts_triads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)

```

### Add Effects

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm_M0 <- sienaAlgorithmCreate(projname = "./results/Collab_M0")
ans_M0 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, returnDeps = TRUE)
ans_M0

fsave(ans_M0, file = "-ans_M0")

# if necessary estimate again!  
# ans_M1_2 <- siena07(myAlgorithm, data = mydata, effects = myeff, prevans_ = ans_M1, returnDeps=TRUE)
# ans_M1_2
```

```{r, echo=FALSE}

ans_M0 <- fload("./results/processed/20241024-ans_M0.rda")
ans_M0
```

### Goodness of Fit

```{r}
GOF <- sienaGOF(ans_M0, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")
```

## Model 1

This model includes the relevant network statistics: InPop, outAct,
isolateNet. It has a convergence of 0.17 and a Goodness of Fit on the
indegree distribution of 0.016. Indegree Popularity (inPop) is defined
as the extent to which people who have a lot of indegrees are more
popular to connect with. This parameter is 0.18, meaning that actors
have a preference to connect with actors who have a lot of indegrees.
The parameter is significant for an alpha of 0.05. Outdegree Activity
(outAct) has a value of -0.13, but is not significant. IsolateNet is
significant andhas a value of 3.91 and refers to the preference of
remaining an isolate. As this value is positive, it means that people
prefer to be an isolate in the network.

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Make Siena df ----
mydata_M1 <- sienaDataCreate(net)

```

### Create Effects object

```{r}
myeff_M1 <- getEffects(mydata_M1)
print01Report(mydata_M1, modelname = "./results/Collab_M1")

# ts_dyads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)
# ts_triads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)

```

### Add Effects

```{r}
myeff_M1 <- includeEffects(myeff_M1, isolateNet, inPop, outAct)
```

### Create and Run the Algorithm

```{r, eval=FALSE}

myAlgorithm_M1 <- sienaAlgorithmCreate(projname = "./results/Collab_M1")
ans_M1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, returnDeps = TRUE)
ans_M1

# fsave(ans_M1, file = "-ans_M1")

# if necessary estimate again!  
# ans_M1_2 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, prevAns = ans_M1, returnDeps=TRUE)
# ans_M1_2

# fsave(ans_M1_2, file = "-ans_M1_2")

```

```{r, echo=FALSE}

ans_M1 <- fload("./results/processed/20241024-ans_M1_2.rda")
ans_M1

```

### Goodness of Fit

```{r}
GOF <- sienaGOF(ans_M1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")
```

## Model 2 - Add Gender (dropped)

Model 2 builds on Model 1 and includes the network statistics for
gender: diffX, diffXTransTrip, egoX & altX. This model has a convergence
of 0.23 and a Goodness of Fit on the indegree distribution of 0.184. For
the structural network statistics we find similar results, in terms of
estimate size and significance, as in Model 1. However, the outdegree
activity parameter almost reaches significance (`r -0.2656 / 0.1550`).
With regard to the covariate network statistics, we find that the gender
of ego (egoX), the gender of alter (altX) and the difference between ego
and alter (diffX) is not significant and thus the estimate cannot be
trusted. The transtrip for different gender (diffXTransTrip) is positive
and significant, which implies that an ego prefers to close triads with
alters who have a different gender score than theirs. This is an
interesting finding, because it implies that their is a tendency towards
diverse collaboration. However, when compared to the level of gender
clustering and the fact that this clustering decreased, this finding
does make sense.

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Independent ----
gender <- df_ego$perc_female
gender <- coCovar(gender)


#---- Make Siena df ----
mydata_M2 <- sienaDataCreate(net, gender)
```

### Create Effects object

```{r}
myeff_M2 <- getEffects(mydata_M2)
print01Report(mydata_M2, modelname = "./results/Collab_M2")

```

### Add Effects

```{r}

myeff_M2 <- includeEffects(myeff_M2, isolateNet, inPop, outAct)

```

```{r}

myeff_M2 <- includeEffects(myeff_M2, diffX, diffXTransTrip, egoX, altX, interaction1 = "gender")

```

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm_M2 <- sienaAlgorithmCreate(projname = "./results/Collab_M2")
ans_M2 <- siena07(myAlgorithm_M2, data = mydata_M2, effects = myeff_M2, returnDeps = TRUE)
ans_M2

# fsave(ans_M2, file = "-ans_M2")


# if necessary estimate again!  
ans_M2_2 <- siena07(myAlgorithm, data = mydata_M2, effects = myeff_M2, prevAns = ans_M2, returnDeps=TRUE)
ans_M2_2
fsave(ans_M2_2, file = "-ans_M2_2")


```

```{r, echo=FALSE}

ans_M2 <- fload("./results/processed/20241024-ans_M2_2.rda")
ans_M2

```

### Goodness of Fit

```{r}
GOF <- sienaGOF(ans_M2, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")

```

## Model 2.5 - Add Gender

Model 2.5 is practically the same model as Model 2, but with inPopSqrt
(indegree popularity squared) instead of inPop. These models were
estimated to check which had the better Goodness of Fit, which according
to the RSiena Manual should be inPopSqrt [@ripley2011manual]. This model
has a convergence ratio of 0.21 and a Goodness of Fit on the indegree
distribution of 0.89, implying a much better fit with the data. Overall,
the estimates of this model were similar to Model 2. There is some
variability in the sizes of the estimates and standard errors, but this
is due to the simulation process, which does not produce identical
estimates. Yet, the general direction of the effect and the significance
is not different between these models and are thus have consistent
findings.

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Independent ----
gender <- df_ego$perc_female
gender <- coCovar(gender)


#---- Make Siena df ----
mydata_M2.5 <- sienaDataCreate(net, gender)
```

### Create Effects object

```{r}
myeff_M2.5 <- getEffects(mydata_M2.5)
print01Report(mydata_M2.5, modelname = "./results/Collab_M2.5")

```

### Add Effects

```{r}
myeff_M2.5 <- includeEffects(myeff_M2.5, isolateNet, inPopSqrt, outAct)

```

```{r}
myeff_M2.5 <- includeEffects(myeff_M2.5, diffX, diffXTransTrip, egoX, altX, interaction1 = "gender")

```

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm_M2.5 <- sienaAlgorithmCreate(projname = "./results/Collab_M2.5")
ans_M2.5 <- siena07(myAlgorithm_M2.5, data = mydata_M2.5, effects = myeff_M2.5, returnDeps = TRUE)
ans_M2.5

fsave(ans_M2.5, file = "-ans_M2.5")

# if necessary estimate again!  
# ans_M2.5_2 <- siena07(myAlgorithm, data = mydata, effects = myeff_M2.5, prevAns = ans_M2.5, returnDeps=TRUE)
# ans_M2.5_2
# fsave(ans_M2.5_2, file = "-ans_M2.5_2")


```

```{r, echo=FALSE}

ans_M2.5 <- fload("./results/processed/20241024-ans_M2.5.rda")
ans_M2.5

```

### Goodness of Fit

```{r}
GOF <- sienaGOF(ans_M2.5, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")

```

## Model 3 - Add Prestige

Model 3 includes the covariate network statistics for Prestige: egoX,
altX and inPopX. This model has a convergence ratio of 0.23 and a a
Goodness of Fit on the indegree distribution of 0.64. In this model, the
parameters for density and reciprocity are still significant, with
values of -1.98 (se = 0.71) and 2.59 (se = 0.38) respectively, meaning
that actors prefer sparse networks, but do prefer to send ties to alters
who have sent ties to them. IsolateNet is still significant with a value
of 3.23 (se = 1.06), implying that actors prefer to be isolates. In this
model, indegree popularity squared (b = 0.17, se = 0.21) is no longer
significant, implying that this might be explained by other network
statistics in the model. The covariate statistics for gender show
similar findings as Model 2 & Model 2.5, namely that actors prefer to
close triads with alters that have a different score for gender (b =
1.51, se = 0.44). the ego effect and alter effect for gender are
non-significant, as was the case in Model 2 & Model 2.5.\
  Lastly, Model 3 shows some significant results with regards to the
covariate network statistics for prestige. The prestige effect for
alters is positive, implying that people prefer to send ties to people
who have a higher amount of prestige (b = 0.042, se = 0.0089).
Additionally, the prestige effect for egos is negative, which indicates
that people who have higher prestige send less ties (b = -0.030, se =
0.015). This is in line with theories of preferential attachment and
upward mobility, because as egos with higher prestige will are more
likely to receive request for collaboration rather then sending request
for collaboration. Interestingly enough, the indegree popularity
statistic for prestige is not significant (b = -0.012, se = 0.023),
implying that actors who are more prestigious do not receive more
indegrees.

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Independent ----
gender <- df_ego$perc_female
gender <- coCovar(gender)

prestige <- df_ego %>% select(Q1.W1, Q1.W2) %>% mutate(mean_pres = (Q1.W1 + Q1.W2)/2)
prestige <- prestige$mean_pres
prestige <- coCovar(prestige)

# h_index <- df_ego$h_index
# h_index <- coCovar(h_index)

#---- Make Siena df ----
mydata_M3 <- sienaDataCreate(net, gender, prestige)#, h_index)

```

### Create Effects object

```{r}
myeff_M3 <- getEffects(mydata_M3)
print01Report(mydata_M3, modelname = "./results/Collab_M3")

# ts_dyads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)
# ts_triads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)

```

### Add Effects

```{r}
myeff_M3 <- includeEffects(myeff_M3, isolateNet, inPopSqrt, outAct)
```

```{r}
myeff_M3 <- includeEffects(myeff_M3, diffX, diffXTransTrip, egoX, altX, interaction1 = "gender")
myeff_M3 <- includeEffects(myeff_M3, egoX, altX, inPopX, interaction1 = "prestige")
# myeff_M3 <- includeEffects(myeff_M3, altX, inpopX, interaction1 = "h_index")

```

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm_M3 <- sienaAlgorithmCreate(projname = "./results/Collab_M3")
ans_M3 <- siena07(myAlgorithm_M3, data = mydata_M3, effects = myeff_M3, returnDeps = TRUE)
ans_M3

fsave(ans_M3, file = "-ans_M3")

# if necessary estimate again!  
ans_M3_2 <- siena07(myAlgorithm_M3, data = mydata_M3, effects = myeff_M3, prevAns = ans_M3, returnDeps=TRUE)
ans_M3_2
# fsave(ans_M3_2, file = "-ans_M3")

```

```{r, echo=FALSE}

ans_M3 <- fload("./results/processed/20241029-ans_M3.rda")
ans_M3

```

```{r, echo=FALSE}

ans_M3_strange <- fload("./results/processed/20241023-ans_M3(weird).rda")
ans_M3_strange

```

### Goodness of Fit

```{r}
GOF <- sienaGOF(ans_M3, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")

```

## Model 4 - Full Model (dropped)

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Independent ----
# gender <- df_ego$perc_female
# gender <- coCovar(gender)
# 
# prestige <- df_ego %>% select(Q1.W1, Q1.W2) %>% mutate(mean_pres = (Q1.W1 + Q1.W2)/2)
# prestige <- prestige$mean_pres
# prestige <- coCovar(prestige)
# 
# h_index <- df_ego$h_index
# h_index <- coCovar(h_index)

ethnicity <- df_ego$ethnicity
ethnicity <- coCovar(ethnicity)

career_age <- 2024 - df_ego$first_year_pub
career_age <- coCovar(career_age)

#---- Make Siena df ----
mydata_M4 <- sienaDataCreate(net, gender, prestige, ethnicity, career_age)

```

### Create Effects object

```{r}
myeff_M4 <- getEffects(mydata_M4)
print01Report(mydata_M4, modelname = "./results/Collab_M4")

# ts_dyads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)
# ts_triads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)

```

### Add Effects

```{r}
myeff_M4 <- includeEffects(myeff_M4, isolateNet, inPopSqrt, outAct)
```

```{r}
myeff_M4 <- includeEffects(myeff_M4, diffX, diffSqX, egoX, altX, interaction1 = "gender")
myeff_M4 <- includeEffects(myeff_M4, altX, inPopX, interaction1 = "prestige")
# myeff_M4 <- includeEffects(myeff_M4, altX, inpopX, interaction1 = "h_index")
myeff_M4 <- includeEffects(myeff_M4, sameX, interaction1 = "ethnicity")
myeff_M4 <- includeEffects(myeff_M4, altX, egoX, interaction1 = "career_age")


```

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm_M4 <- sienaAlgorithmCreate(projname = "./results/Collab_M4")
ans_M4 <- siena07(myAlgorithm_M4, data = mydata_M4, effects = myeff_M4, returnDeps = TRUE)
ans_M4

# fsave(ans_M4, file = "-ans_M4")

# if necessary estimate again!  
# ans_M2_2 <- siena07(myAlgorithm, data = mydata, effects = myeff, prevans_ = ans_M1, returnDeps=TRUE)
# ans_M2_2
```

```{r, echo=FALSE}

# ans_M4 <- fload("./results/processed/20241024-ans_M4.rda")
# ans_M4

```

### Goodness of Fit

```{r}
# GOF <- sienaGOF(ans_M4, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

# plot(GOF, main = "")
```

## Model 5 - Interaction Model

Model 5, the final model, contains the network statistics of Model 3,
and includes an interaction term for gender \* prestige. This
interaction term was centered beforehand to ensure that there was still
a meaningful 0 (i.e. the prestige score of male sociologists). This way,
the model will estimate how the prestige of female sociologists
influences the network, using the following network statistics: egoX,
altX, inPopX & diffXTransTrip. This model has a convergence of 0.22 and
a Goodness of Fit for the indegree distribution of 0.77. With regard to
the structural effects, there are only significant estimates for
reciprocity (b = 2.62, se = 0.39) and isolateNet (b = 3.46, se = 1.58).
The parameter estimates of density, outdegree activity and indegree
popularity could not be precisely determined in Model 5.\
  Regarding the covariate network statistics, there are no significant
estimates, apart from the alter prestige effect (b = 0.067, se = 0.028)
and the diffXTransTrip statistic of the interaction term (b = 1.14, se =
0.48). The latter indicates that actors prefer to close triads with
female alters who have a different level of prestige. This finding seem
to imply that female prestige decreases gender clustering in
collaboration networks, which is in line with *hypothesis 3.*
Additionally, given the significant estimate for the prestige of alters,
it seems to be the case that, at Radboud University and Utrecht
Univeristy, prestige is a more imporant indicator of collaboration than
gender. Combined with the findings of Model 3, there is some evidence
that indicates that the collaboration network is becoming more
egalitarian and thus *hypothesis 3* does not need to be rejected.
However, given the diverse findings and lack of significant parameters
across the models, the findings should be interpreted with caution.

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Independent ----
gender <- df_ego$perc_female
G_cent <- gender - mean(gender, na.rm = T)
gender <- coCovar(gender)

prestige <- df_ego %>% select(Q1.W1, Q1.W2) %>% mutate(mean_pres = (Q1.W1 + Q1.W2)/2)
prestige <- prestige$mean_pres
P_cent <- prestige - mean(prestige)

prestige <- coCovar(prestige)


IT_PxG <- P_cent * G_cent
IT_PxG <- coCovar(IT_PxG, centered = FALSE)


#---- Make Siena df ----
mydata_M5 <- sienaDataCreate(net, gender, prestige, IT_PxG)

```

### Create Effects object

```{r}
myeff_M5 <- getEffects(mydata_M5)
print01Report(mydata_M5, modelname = "./results/Collab_M5")

# ts_dyads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)
# ts_triads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)

```

### Add Effects

```{r}
myeff_M5 <- includeEffects(myeff_M5, isolateNet, inPopSqrt, outAct)
```

```{r}
myeff_M5 <- includeEffects(myeff_M5, diffX, diffXTransTrip, egoX, altX, interaction1 = "gender")
myeff_M5 <- includeEffects(myeff_M5, egoX, altX, inPopX, interaction1 = "prestige")
myeff_M5 <- includeEffects(myeff_M5, egoX, altX, inPopX, diffXTransTrip, interaction1 = "IT_PxG")

# myeff_M3 <- includeEffects(myeff_M3, altX, inpopX, interaction1 = "h_index")

```

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm_M5 <- sienaAlgorithmCreate(projname = "./results/Collab_M5")
ans_M5 <- siena07(myAlgorithm_M5, data = mydata_M5, effects = myeff_M5, returnDeps = TRUE)
ans_M5

# fsave(ans_M5, file = "-ans_M5")

# if necessary estimate again!  
ans_M5_2 <- siena07(myAlgorithm_M5, data = mydata_M5, effects = myeff_M5, prevAns = ans_M5, returnDeps=TRUE)
ans_M5_2
# fsave(ans_M5_2, file = "-ans_M5")

```

```{r, echo=FALSE}
ans_M5 <- fload("results/processed/20241029-ans_M5.rda")
ans_M5
```
### Goodness of Fit
```{r}
GOF <- sienaGOF(ans_M5, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")
```
