---
title: "RSiena Behavioural Models"
#bibliography: references.bib
author: "Niels Vullings"
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: 72
---

```{r, echo=FALSE}
rm(list = ls())
```

# Load UDF

```{r}
colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}

fsave <- function(x, file = NULL, location = "./results/processed/") {
  ifelse(!dir.exists("results"), dir.create("data"), FALSE)
  ifelse(!dir.exists("results/processed"), dir.create("results/processed"), FALSE)
  if (is.null(file))
    file = deparse(substitute(x))
  datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
  totalname <- paste(location, datename, file, ".rda", sep = "")
  save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
  load(filename)
  get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
  knitr::kable(x, digits = 2, "html", ...) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
    kableExtra::scroll_box(width = "100%", height = "300px")
}

```

# Load Packages

```{r, warning=FALSE, results='hide', message=FALSE}
packages <- c("tidyverse", "sna", "igraph", "RSiena", "iterators", "doParallel")

fpackage.check(packages)

```

# Load Data

```{r}
# Load Ego data
load("data/processed/RU_UU_ego.RData")

# Load Works data
load("data/processed/RU_UU_works.RData")

# Load raw data for networks
load("data/processed/soc_data_raw.RData")
```

# Make network data for RSiena

```{r}
print(paste0("", dim(soc_data$nets)))

wave_1 <- soc_data$nets[1,,]
diag(wave_1) <- 0

wave_2 <- soc_data$nets[2,,]
diag(wave_2) <- 0

net_soc_array <- array(data = c(wave_1, wave_2), dim = c(dim(wave_1), 2))
dim(net_soc_array)
```

# Analysis {.tabset}

Originally, my idea for this study was to see how prestige changes based
on specific network structures. I soon realized that this would be to
advanced for my current understanding of both Social Networks and
RSiena, to make that happen. That is why in this section, I will use
Model 2.5 of my study to see how prestige changes based on the gender
covariate network statistics. As behavioural statistics, I added
indegree isolates and outdegree isolates effects and the total
similarity x alter popularity statistic. To my understanding, this
statistic Unfortunately, after trying several times, I was not able to
get the model to converge. Therefore, I just included one of the models
to show the output.

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

Beh_pres <- df_ego %>% select(Q1.W1, Q1.W2) %>% as.matrix()

Beh_pres <- sienaDependent(Beh_pres, type = "behavior")

#---- Independent ----
gender <- df_ego$perc_female

gender <- coCovar(gender)

#---- Make Siena df ----
mydata_Beh <- sienaDataCreate(net, Beh_pres, gender)
```

### Create Effects object

```{r}
myeff_Beh <- getEffects(mydata_Beh)
print01Report(mydata_Beh, modelname = "./results/Collab_Beh")

```

### Add Effects

```{r}
myeff_Beh <- includeEffects(myeff_Beh, isolateNet, inPopSqrt, outAct)

```

```{r}
myeff_Beh <- includeEffects(myeff_Beh, diffX, diffXTransTrip, egoX, altX, interaction1 = "gender")
myeff_Beh <- includeEffects(myeff_Beh, name = "Beh_pres", totSimPopAlt, isolate,  interaction1 = "net")
myeff_Beh <- includeEffects(myeff_Beh, name = "Beh_pres", effFrom, interaction1 = "gender")

```

### Create and Run the Algorithm

#### Set up parallel cluster

```{r, results='hide'}
no_cores <- detectCores() - 1
mycl <- makeCluster(rep("localhost", no_cores))
clusterEvalQ(mycl, library(RSiena))
registerDoParallel(mycl)
# stopCluster(mycl)

```

```{r, eval=FALSE}
myAlgorithm_Beh <- sienaAlgorithmCreate(projname = "./results/Collab_Beh")
ans_Beh1 <- siena07(myAlgorithm_Beh, useCluster = T, nbrNodes = no_cores, data = mydata_Beh, effects = myeff_Beh, returnDeps = TRUE)
ans_Beh1
# fsave(ans_Beh1, file = "-ans_Beh1")

ans_Beh2 <- siena07(myAlgorithm_Beh, useCluster = T, nbrNodes = no_cores, data = mydata_Beh, effects = myeff_Beh, returnDeps = TRUE)
ans_Beh2
# fsave(ans_Beh2, file = "-ans_Beh2")

ans_Beh3 <- siena07(myAlgorithm_Beh, useCluster = T, nbrNodes = no_cores, data = mydata_Beh, effects = myeff_Beh, returnDeps = TRUE)
ans_Beh3
# fsave(ans_Beh3, file = "-ans_Beh3")

ans_Beh4 <- siena07(myAlgorithm_Beh, useCluster = T, nbrNodes = no_cores, data = mydata_Beh, effects = myeff_Beh, returnDeps = TRUE)
ans_Beh4
# fsave(ans_Beh4, file = "-ans_Beh4")

ans_Beh5 <- siena07(myAlgorithm_Beh, useCluster = T, nbrNodes = no_cores, data = mydata_Beh, effects = myeff_Beh, returnDeps = TRUE)
ans_Beh5
# fsave(ans_Beh5, file = "-ans_Beh5")


# stopCluster(mycl)


# if necessary estimate again!  
ans_Beh_2 <- siena07(myAlgorithm_Beh, data = mydata_Beh, effects = myeff_Beh, prevAns = ans_Beh1, returnDeps=TRUE)
ans_Beh_2
fsave(ans_Beh_2, file = "-ans_Beh_2")


```

```{r, echo=FALSE}

ans_Beh <- fload("./results/processed/20241030-ans_Beh1.rda")
ans_Beh

```

### Goodness of Fit

```{r}
# GOF <- sienaGOF(ans_Beh, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

# plot(GOF, main = "")

```
