---
title: "Results - RSiena Models"
#bibliography: references.bib
author: "Niels Vullings"
bibliography: references.bib
editor_options: 
  markdown: 
    wrap: 72
---

```{r, echo=FALSE}
rm(list = ls())
```

# Load UDF

```{r}
colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

fpackage.check <- function(packages) {
  lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
      install.packages(x, dependencies = TRUE)
      library(x, character.only = TRUE)
    }
  })
}

fsave <- function(x, file = NULL, location = "./results/processed/") {
  ifelse(!dir.exists("results"), dir.create("data"), FALSE)
  ifelse(!dir.exists("results/processed"), dir.create("results/processed"), FALSE)
  if (is.null(file))
    file = deparse(substitute(x))
  datename <- substr(gsub("[:-]", "", Sys.time()), 1, 8)
  totalname <- paste(location, datename, file, ".rda", sep = "")
  save(x, file = totalname)  #need to fix if file is reloaded as input name, not as x. 
}

fload <- function(filename) {
  load(filename)
  get(ls()[ls() != "filename"])
}

fshowdf <- function(x, ...) {
  knitr::kable(x, digits = 2, "html", ...) %>%
    kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
    kableExtra::scroll_box(width = "100%", height = "300px")
}

```

# Load Packages

```{r, warning=FALSE, results='hide', message=FALSE}
packages <- c("tidyverse", "sna", "igraph", "RSiena", "iterators", "doParallel")

fpackage.check(packages)

```

# Load Data

```{r}
# Load Ego data
load("data/processed/RU_UU_ego.RData")

# Load Works data
load("data/processed/RU_UU_works.RData")

# Load raw data for networks
load("data/processed/soc_data_raw.RData")
```

# Make network data for RSiena

```{r}
print(paste0("", dim(soc_data$nets)))

wave_1 <- soc_data$nets[1,,]
diag(wave_1) <- 0

wave_2 <- soc_data$nets[2,,]
diag(wave_2) <- 0

net_soc_array <- array(data = c(wave_1, wave_2), dim = c(dim(wave_1), 2))
dim(net_soc_array)
```

# Analysis {.tabset}

## Model 0
TEXT

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Make Siena df ----
mydata <- sienaDataCreate(net)
```

### Create Effects object

```{r}
myeff_M0 <- getEffects(mydata)
print01Report(mydata, modelname = "./results/Collab_M0")

# ts_dyads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)
# ts_triads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)

```

### Add Effects

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm <- sienaAlgorithmCreate(projname = "./results/Collab_M0")
ans_M0 <- siena07(myAlgorithm, data = mydata, effects = myeff_M0, returnDeps = TRUE)
ans_M0

fsave(ans_M0, file = "-ans_M0")

# if necessary estimate again!  
# ans_M1_2 <- siena07(myAlgorithm, data = mydata, effects = myeff, prevans_ = ans_M1, returnDeps=TRUE)
# ans_M1_2
```

```{r, echo=FALSE}

ans_M0 <- fload("./results/processed/20241024-ans_M0.rda")
ans_M0
```

### Goodness of Fit

```{r}
GOF <- sienaGOF(ans_M0, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")
```

## Model 1
TEXT


### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Make Siena df ----
mydata <- sienaDataCreate(net)
```

### Create Effects object

```{r}
myeff_M1 <- getEffects(mydata)
print01Report(mydata, modelname = "./results/Collab_M1")

# ts_dyads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)
# ts_triads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)

```

### Add Effects

```{r}
myeff_M1 <- includeEffects(myeff_M1, isolateNet, inPop, outAct)
```

### Create and Run the Algorithm

```{r, eval=FALSE}

myAlgorithm <- sienaAlgorithmCreate(projname = "./results/Collab_M1")
ans_M1 <- siena07(myAlgorithm, data = mydata, effects = myeff_M1, returnDeps = TRUE)
ans_M1

# fsave(ans_M1, file = "-ans_M1")

# if necessary estimate again!  
ans_M1_2 <- siena07(myAlgorithm, data = mydata, effects = myeff_M1, prevAns = ans_M1, returnDeps=TRUE)
ans_M1_2

fsave(ans_M1_2, file = "-ans_M1_2")

```

```{r, echo=FALSE}

ans_M1 <- fload("./results/processed/20241024-ans_M1_2.rda")
ans_M1

```

### Goodness of Fit

```{r}
GOF <- sienaGOF(ans_M1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")
```

## Model 2 - Add Gender (dropped)
TEXT 

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Independent ----
gender <- df_ego$perc_female
gender <- coCovar(gender)


#---- Make Siena df ----
mydata <- sienaDataCreate(net, gender)
```

### Create Effects object

```{r}
myeff_M2 <- getEffects(mydata)
print01Report(mydata, modelname = "./results/Collab_M2")

```

### Add Effects

```{r}

myeff_M2 <- includeEffects(myeff_M2, isolateNet, inPop, outAct)

```

```{r}

myeff_M2 <- includeEffects(myeff_M2, diffX, diffXTransTrip, egoX, altX, interaction1 = "gender")

```

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm <- sienaAlgorithmCreate(projname = "./results/Collab_M2")
ans_M2 <- siena07(myAlgorithm, data = mydata, effects = myeff_M2, returnDeps = TRUE)
ans_M2

# fsave(ans_M2, file = "-ans_M2")


# if necessary estimate again!  
ans_M2_2 <- siena07(myAlgorithm, data = mydata, effects = myeff_M2, prevAns = ans_M2, returnDeps=TRUE)
ans_M2_2
fsave(ans_M2_2, file = "-ans_M2_2")


```

```{r, echo=FALSE}

ans_M2 <- fload("./results/processed/20241024-ans_M2_2.rda")
ans_M2

```

### Goodness of Fit

```{r}
GOF <- sienaGOF(ans_M2, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")

```

## Model 2.5 - Add Gender
TEXT 

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Independent ----
gender <- df_ego$perc_female
gender <- coCovar(gender)


#---- Make Siena df ----
mydata <- sienaDataCreate(net, gender)
```

### Create Effects object

```{r}
myeff_M2.5 <- getEffects(mydata)
print01Report(mydata, modelname = "./results/Collab_M2.5")

```

### Add Effects

```{r}
myeff_M2.5 <- includeEffects(myeff_M2.5, isolateNet, inPopSqrt, outAct)

```

```{r}
myeff_M2.5 <- includeEffects(myeff_M2.5, diffX, diffXTransTrip, egoX, altX, interaction1 = "gender")

```

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm <- sienaAlgorithmCreate(projname = "./results/Collab_M2.5")
ans_M2.5 <- siena07(myAlgorithm, data = mydata, effects = myeff_M2.5, returnDeps = TRUE)
ans_M2.5

fsave(ans_M2.5, file = "-ans_M2.5")

# if necessary estimate again!  
# ans_M2.5_2 <- siena07(myAlgorithm, data = mydata, effects = myeff_M2.5, prevAns = ans_M2.5, returnDeps=TRUE)
# ans_M2.5_2
# fsave(ans_M2.5_2, file = "-ans_M2.5_2")


```

```{r, echo=FALSE}

ans_M2.5 <- fload("./results/processed/20241024-ans_M2.5.rda")
ans_M2.5

```

### Goodness of Fit

```{r}
GOF <- sienaGOF(ans_M2.5, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")

```

## Model 3 - Add Prestige
TEXT 

### Create SienaData

```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Independent ----
# gender <- df_ego$perc_female
# gender <- coCovar(gender)

prestige <- df_ego %>% select(Q1.W1, Q1.W2) %>% mutate(mean_pres = (Q1.W1 + Q1.W2)/2)
prestige <- prestige$mean_pres
prestige <- coCovar(prestige)

# h_index <- df_ego$h_index
# h_index <- coCovar(h_index)

#---- Make Siena df ----
mydata_M3 <- sienaDataCreate(net, gender, prestige)#, h_index)

```

### Create Effects object

```{r}
myeff_M3 <- getEffects(mydata)
print01Report(mydata, modelname = "./results/Collab_M3")

# ts_dyads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)
# ts_triads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)

```

### Add Effects

```{r}
myeff_M3 <- includeEffects(myeff_M3, isolateNet, inPopSqrt, outAct)
```

```{r}
myeff_M3 <- includeEffects(myeff_M3, diffX, diffXTransTrip, egoX, altX, interaction1 = "gender")
myeff_M3 <- includeEffects(myeff_M3, altX, inPopX, interaction1 = "prestige")
# myeff_M3 <- includeEffects(myeff_M3, altX, inpopX, interaction1 = "h_index")

```

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm_M3 <- sienaAlgorithmCreate(projname = "./results/Collab_M3")
ans_M3 <- siena07(myAlgorithm, data = mydata, effects = myeff_M3, returnDeps = TRUE)
ans_M3

fsave(ans_M3, file = "-ans_M3")

# if necessary estimate again!  
# ans_M3_2 <- siena07(myAlgorithm, data = mydata, effects = myeff_M3, prevAns = ans_M3, returnDeps=TRUE)
# ans_M3_2
# fsave(ans_M2_2, file = "-ans_M2_2")

```

```{r, echo=FALSE}

ans_M3 <- fload("./results/processed/20241024-ans_M3.rda")
ans_M3

```

```{r, echo=FALSE}

ans_M3_strange <- fload("./results/processed/20241023-ans_M3(weird).rda")
ans_M3_strange

```

### Goodness of Fit
```{r}
GOF <- sienaGOF(ans_M3, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")

GOF_str <- sienaGOF(ans_M3_strange, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF_str, main = "")
```

### Relative Influence
```{r}
# RI_M3 <- sienaRI(data = mydata_M3,ans = ans_M3)
```

## Model 4 - Full Model (dropped)
 

### Create SienaData

```{r}
#---- Dependent ----
# net <- sienaDependent(net_soc_array)

#---- Independent ----
# gender <- df_ego$perc_female
# gender <- coCovar(gender)
# 
# prestige <- df_ego %>% select(Q1.W1, Q1.W2) %>% mutate(mean_pres = (Q1.W1 + Q1.W2)/2)
# prestige <- prestige$mean_pres
# prestige <- coCovar(prestige)
# 
# h_index <- df_ego$h_index
# h_index <- coCovar(h_index)

ethnicity <- df_ego$ethnicity
ethnicity <- coCovar(ethnicity)

career_age <- 2024 - df_ego$first_year_pub
career_age <- coCovar(career_age)

#---- Make Siena df ----
mydata <- sienaDataCreate(net, gender, prestige, ethnicity, career_age)

```

### Create Effects object

```{r}
myeff_M4 <- getEffects(mydata)
print01Report(mydata, modelname = "./results/Collab_M4")

# ts_dyads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)
# ts_triads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)

```

### Add Effects

```{r}
myeff_M4 <- includeEffects(myeff_M4, isolateNet, inPopSqrt, outAct)
```

```{r}
myeff_M4 <- includeEffects(myeff_M4, diffX, diffSqX, egoX, altX, interaction1 = "gender")
myeff_M4 <- includeEffects(myeff_M4, altX, inPopX, interaction1 = "prestige")
# myeff_M4 <- includeEffects(myeff_M4, altX, inpopX, interaction1 = "h_index")
myeff_M4 <- includeEffects(myeff_M4, sameX, interaction1 = "ethnicity")
myeff_M4 <- includeEffects(myeff_M4, altX, egoX, interaction1 = "career_age")


```

### Create and Run the Algorithm

```{r, eval=FALSE}
myAlgorithm_M4 <- sienaAlgorithmCreate(projname = "./results/Collab_M4")
ans_M4 <- siena07(myAlgorithm, data = mydata, effects = myeff_M4, returnDeps = TRUE)
ans_M4

fsave(ans_M4, file = "-ans_M4")

# if necessary estimate again!  
# ans_M2_2 <- siena07(myAlgorithm, data = mydata, effects = myeff, prevans_ = ans_M1, returnDeps=TRUE)
# ans_M2_2
```

```{r, echo=FALSE}

ans_M4 <- fload("./results/processed/20241024-ans_M4.rda")
ans_M4

```

### Goodness of Fit

```{r}
GOF <- sienaGOF(ans_M4, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")
```


## Model 5 - Interaction Model
 

### Create SienaData
```{r}
#---- Dependent ----
net <- sienaDependent(net_soc_array)

#---- Independent ----
gender <- df_ego$perc_female
G_cent <- gender - mean(gender, na.rm = T)
gender <- coCovar(gender)

prestige <- df_ego %>% select(Q1.W1, Q1.W2) %>% mutate(mean_pres = (Q1.W1 + Q1.W2)/2)
prestige <- prestige$mean_pres
P_cent <- prestige - mean(prestige)

prestige <- coCovar(prestige)


IT_PxG <- P_cent * G_cent
IT_PxG <- coCovar(IT_PxG, centered = FALSE)


#---- Make Siena df ----
mydata_M5 <- sienaDataCreate(net, gender, prestige, IT_PxG)

```

### Create Effects object
```{r}
myeff_M5 <- getEffects(mydata_M5)
print01Report(mydata, modelname = "./results/Collab_M5")

# ts_dyads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)
# ts_triads_evo(sims = wave_2, net1 = wave_1, forplot = TRUE)

```

### Add Effects
```{r}
myeff_M5 <- includeEffects(myeff_M5, isolateNet, inPopSqrt, outAct)
```

```{r}
myeff_M5 <- includeEffects(myeff_M5, diffX, diffXTransTrip, egoX, altX, interaction1 = "gender")
myeff_M5 <- includeEffects(myeff_M5, altX, inPopX, interaction1 = "prestige")
myeff_M5 <- includeEffects(myeff_M5, altX, inPopX, interaction1 = "IT_PxG")

# myeff_M3 <- includeEffects(myeff_M3, altX, inpopX, interaction1 = "h_index")

```

### Create and Run the Algorithm
```{r, eval=FALSE}
myAlgorithm_M5 <- sienaAlgorithmCreate(projname = "./results/Collab_M5")
ans_M5 <- siena07(myAlgorithm_M5, data = mydata_M5, effects = myeff_M5, returnDeps = TRUE)
ans_M5

# fsave(ans_M5, file = "-ans_M5")

# if necessary estimate again!  
ans_M5_2 <- siena07(myAlgorithm_M5, data = mydata_M5, effects = myeff_M5, prevAns = ans_M5, returnDeps=TRUE)
ans_M5_2
# fsave(ans_M5_2, file = "-ans_M5")

```

```{r, echo=FALSE}
ans_M5 <- fload("results/processed/20241025-ans_M5.rda")

```

```{r}
GOF <- sienaGOF(ans_M5, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "net")

plot(GOF, main = "")
```

```{r}
# egoX, altX voor career_age
# sameX voor ethnicity
```


```{r}
# sessionInfo()
# SienaRI - 1.3.14
#Rsiena Schatten, ANS opslaan, code chunk, evaluate = FALSE, inladen siena object, die echo = FALSE
# Alle cache folder leeghalen op het moment dat iets foutgaat met wegschrijven of inladen
```
