---
title: "Journal - Week 1"
#bibliography: references.bib
author: "Niels Vullings"
bibliography: references.bib
---

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(tidy.opts=list(width.cutoff=100),tidy=TRUE, warning = FALSE, message = FALSE,comment = "#>", cache=TRUE, class.source=c("test"), class.output=c("test2"))
options(width = 100)
rgl::setupKnitr()



colorize <- function(x, color) {sprintf("<span style='color: %s;'>%s</span>", color, x) }

```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
# klippy::klippy(color = 'darkgreen')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

Last compiled on `r format(Sys.time(), '%B, %Y')`

<br>

------------------------------------------------------------------------

# Assignment Week 1

<br>


## Research Questions

Inequalities are omnipresent in society and this does not exclude the academic world. Be it conscious or subconscious, our actions are in part shaped by bias and stereotypes (author, year). One of the most dividing lines in the 21st century is that of gender. Even within the social sciences, men and women do not receive the same treatment and grants, publications and upper academic positions are unequally distributed [@bellotti2022]. This concept of academic inequality has been called the *Matilda effect*, named after the *Matthew effect*, named by Robert Merton. Bellotti et al. (2022) studied the composition of male and female collaboration networks in Italy. They find persisting inequalities between men and women in terms of research funding and collaboration across all academic disciplines. They argue that their findings are generalisable to fields where collaboration is key to succes.

In a study that looked at the impact that networks have on gender differences in coauthorship, it was found that representation of women matters in relation to their network access [@mcdowell2006a]. The study looked at how male and female economist PhD's have access in their networks for publications and co-authorship. They find that over time, women are less likely to coauthor and publish articles compared to men. However, they also find that this probability does dwindle by 1993. When other forms of gender differences are included, women are less likely to be "successful" in academics.

-   RQ 1: To what extent has gender segregation of publication networks in the Dutch sociology departments changed between `r colorize("timepoint 1", "red")` and `r colorize("timepoint 2", "red")`?
-   RQ 2: How has this change in segregation influenced the succes[^1] of female scholars?

[^1]: I define succes as the total amount of citations a scholar has received within that timeframe
